### 2024-10-29 main_widom_morse.tex

\binoppenalty=10000
\relpenalty=10000
\begin{center}
	\renewcommand{\theequation}{\arabic{section}}
	\section*{Crossover line in the supercritical cell fluid model (I haven't thought up a good title yet)}
	\setcounter{equation}{0}
\end{center}

@@

On the other hand, within the present approach, $M=0$ at the points of phase coexistance up to the critical point. Thus, the implementation of the condition  $M=0$ appears to be a natural continuation of the coexistance line into the supercritical region.

>>>>

\binoppenalty=10000
\relpenalty=10000
\begin{center}
	\renewcommand{\theequation}{\arabic{section}}
	\section*{Supercritical Crossover Lines in the Cell Fluid Model}
	\setcounter{equation}{0}
\end{center}

@@

On the one hand, within the present approach, the condition $M=0$ holds along phase coexistence up to the critical point. Thus, the implementation of the condition  $M=0$ above CP seems to be a natural continuation of the coexistence line into the supercritical region. On the other hand, taking into account the functional form of the grand partition function~\cite{KD16,KR09}, the condition of $M=0$ is equivalent to the absence of an external field in the Ising model. This analogy is interesting from the perspective of mapping between the Ising model and fluids~\cite{Kulinskii10jcp,BK11}.
